Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-09 manuscript/manuscript.Rmd
new population model based on poisson likelihood

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated `r nSims` times. Note that the y-axes vary across panels.", fig.width=5, fig.height=6, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_Residuals.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(yearDiff))

ggplot(resD)+
  geom_hline(aes(yintercept=0))+
#   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
#   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
  geom_boxplot(aes(x=year, y=covChangeResiduals), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
  facet_grid(species~., scales = "free_y")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Boxplots of model residuals for one-step-ahead forecasts at each observation year. Each one-step forecast was simulated `r nSims` times. Note that the y-axes vary across panels.", fig.width=5, fig.height=6, cache=FALSE, results='hide'}
resD <- readRDS("../montana/quadBM/simulations/quadBM_oneStep_ResidualsFullModel.rds")
nSims <- length(unique(resD$sim))
diffD <- ddply(resD, c("year", "species"), summarise,
               avgDiff = mean(yearDiff))

ggplot(resD)+
  geom_hline(aes(yintercept=0), linetype=2)+
#   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
#   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
  geom_boxplot(aes(x=year, y=resids), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
  facet_grid(species~., scales = "free_y")+
  xlab("Year")+
  ylab("Residuals (% cover difference)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
